---
title: "p8105_hw1_leb2236"
author: Laura Bulmer
output: github_document
date: "2024-09-21"
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

I installed the package containing the penguin dataset and will now 
load the penguin dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

#### Description of the Penguins dataset

The dataset penguins contains data regarding observed penguins.

The 8 variables included in the dataset are species of penguin ('species'), 
island ('island'), bill 
length in mm ('bill_length_mm'), bill depth in mm ('bill_depth_mm'), flipper
length in mm ('flipper_length_mm'), body mass in grams ('body_mass_g'), 
sex, and year.

In this dataset, there are `r nrow(penguins)` rows/observations
and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), 
na.rm = TRUE)`. 

#### Scatterplot of flipper length vs bill length

We will use the code below to generate the scatter plot and then to save it
as a pdf to our directory.

```{r}
ggplot(penguins, aes(
  x = bill_length_mm, 
  y = flipper_length_mm,
  color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```




