---
title: "p8105_hw1_leb2236"
author: Laura Bulmer
output: github_document
date: "2024-09-21"
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

I installed the package containing the penguin dataset and will now 
load the penguin dataset.

```{r loading_data}
data("penguins", package = "palmerpenguins")
```

#### Description of the Penguins dataset

The dataset penguins contains data regarding observed penguins.

The 8 variables included in the dataset are species of penguin ('species'), 
island ('island'), bill 
length in mm ('bill_length_mm'), bill depth in mm ('bill_depth_mm'), flipper
length in mm ('flipper_length_mm'), body mass in grams ('body_mass_g'), 
sex, and year.

In this dataset, there are `r nrow(penguins)` rows/observations
and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), 
na.rm = TRUE)`. 

#### Scatterplot of flipper length vs bill length

We will use the code below to generate the scatter plot and then to save it
as a pdf to our directory.

```{r plotting}
ggplot(penguins, aes(
  x = bill_length_mm, 
  y = flipper_length_mm,
  color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

# Problem 2

#### Creating the data frame

The code below is used to create a data frame.

```{r creating_df}
homework_df = tibble(
  sample = rnorm(10),
  log_vec = sample > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "low", "low", "medium", "medium",
                        "medium", "high", "high"))
)
```

#### Taking the mean of each variable

```{r taking_the_means}
mean(pull(homework_df, sample))
mean(pull(homework_df, log_vec))
mean(pull(homework_df, char_vec))
mean(pull(homework_df, factor_vec))
```

We are able to take the mean of the sample and the logical vector,
but not the character or factor vectors.

#### Applying the as.numeric function

```{r converting_to_numeric, results = "hide"}
as.numeric(pull(homework_df,log_vec))
as.numeric(pull(homework_df,char_vec))
as.numeric(pull(homework_df,factor_vec))
```

Applying the as.numeric function to these variables had different outcomes. 

* The logical vector was successfully converted, which makes sense as we were 
able to take the mean. 
* The character vector was converted to NAs, which also 
makes sense as we couldn't take the mean for that variable. 
* The factor vector was coverted, however the numbers don't make sense with the 
levels that were set. Given we weren't able to take the mean, I wasn't 
expecting the numeric conversion to work well.It appears they were converted 
based on the alphabetical order of the levels set.
